---
title: "Exercise 4"
author: "Yuting Huang, Jipeng Cheng, Weidi Hou"
date: "5/1/2022"
output: bookdown::html_document2
---

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo=FALSE)
```
# Clustering and PCA
## Clustering
### Color of wines
```{r fig1, fig.align='center', fig.cap="Value of features for wines of different colors", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
library(RCurl)
library(tidyverse)
library(mosaic)
library(LICORS)  # for kmeans++
library(ggplot2)
library(ggpubr)
library(reshape2) # stack data by PC

# Read data #
wine_original = read.csv("https://raw.githubusercontent.com/Cheng-Jipeng/ECO395M/master/data/wine.csv")
wine = wine_original %>% 
  select(-quality,-color) %>% 
  scale(center=TRUE, scale=TRUE) # standardize data


# Clustering #
## Kmean++
wine_clust_color = kmeanspp(wine, k = 2, nstart = 25)
#unique(wine_original$quality)
wine_clust_quality = kmeanspp(wine, k = 7, nstart = 25)
wine_results = data.frame(wine, color = wine_original$color, 
                          quality = wine_original$quality,
                          clust_color = wine_clust_color$cluster,
                          clust_quality = wine_clust_quality$cluster)


# Clustering Assessment #
## Color ##
### Data visualization
wine_plot_data_clust = cbind(wine_results[12:15], stack(wine_results[1:11]))
ggplot(wine_plot_data_clust) +
  geom_boxplot(aes(x=color, y=values)) +
  facet_wrap(~ind, ncol = 3) +
  labs(y = "Value of Chemicals",
       x="Actual Color")# mostly differed by va and tsd
```

Figure \@ref(fig:fig1) shows that colors can be most distinguished by `volatile.acidity` and `total.sulfur.dioxide` since these two features' differences in median are significantly large. After running K-means++, we can find that `volatile.acidity` and `total.sulfur.dioxide` naturally help divide the wines into 2 groups by Figure \@ref(fig:fig2).

```{r fig2, fig.align='center', fig.cap="Features by clusters (color)", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
### Labels emerge naturally from clustering
# refernce: 【7.1】cars.R
ggplot(wine_results) + 
  geom_point(aes(x=volatile.acidity, y=total.sulfur.dioxide,
                 col=factor(clust_color))) +
  labs(color='Generated Cluster') 
```

This can be confirmed by plotting the true color of wines (Figure \@ref(fig:fig3)), which shows group 1 refers to the whites and group 2 refers to the reds.

```{r fig3, fig.align='center', fig.cap="Features by actual labels (color)", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
ggplot(wine_results) + 
  geom_point(aes(x=volatile.acidity, y=total.sulfur.dioxide,
                 col=factor(color))) +
  labs(color='Actual Color')
```

The confusion matrix gives the precision of using K-means++ to differ the reds from the whites.

```{r warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
### Compare cluster and labels
confusion_color = table(y=wine_results$color, yhat=wine_results$clust_color)
confusion_color[2:1,]
```

### Quality of wines
Figure \@ref(fig:fig4) shows that it can be hard to figure out significant chemical differences among wines of different quality. 

```{r fig4, fig.align='center', fig.cap="Value of features for wines of different quality", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
## Quality ##
### Data visualization
ggplot(wine_plot_data_clust) +
  geom_boxplot(aes(x=factor(quality), y=values)) +
  facet_wrap(~ind, ncol = 3) +
  labs(y = "Value of Chemicals", x="Actual Quality")
```

However, if we focus on the feature's median values for wines of different quality as in Figure \@ref(fig:fig5), we may expect that at least `density` and `alcohol` can distinguish wines of high quality from the rest, and `volatile.acidity` and `free.sulfur.dioxide` can differ wines of low quality from others. 

```{r fig5, fig.align='center', fig.cap="Median value of features for wines of different quality", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
#wine_plot_data_clust %>%
#  group_by(quality, ind) %>%
#  summarise(mean_feature = mean(values)) %>%
#  ggplot() +
#  geom_point(aes(x=factor(quality), y=mean_feature)) +
#  facet_wrap(~ind, ncol=3) 
wine_plot_data_clust %>%
  group_by(quality, ind) %>%
  summarise(median_feature = median(values)) %>%
  ggplot() +
  geom_point(aes(x=factor(quality), y=median_feature)) +
  facet_wrap(~ind, ncol = 3) +
  labs(y = "Median Value of Chemicals",
       x="Actual Quality")# mostly differed by chlo and dens, ca and fsd
```

After running K-means++ to divide wines into 7 groups (since the actual quality of wines are only ranged from 3 to 9), we do see the some differences in quality emerge naturally from clustering by Figure \@ref(fig:fig6). 

```{r fig6, fig.align='center', fig.cap="Features by clusters (quality)", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
### Labels emerge naturally from clustering
#### clustering labels 
clust_1 = ggplot(wine_results) + 
  geom_point(aes(x=density, y=alcohol,
                 col=factor(clust_quality))) +
  labs(color="Generated Cluster")
clust_2 = ggplot(wine_results) + 
  geom_point(aes(x=volatile.acidity, y=free.sulfur.dioxide,
                 col=factor(clust_quality))) +
  labs(color="Generated Cluster")
clust_3 = ggplot(wine_results) + 
  geom_point(aes(x=density, y=free.sulfur.dioxide,
                 col=factor(clust_quality))) +
  labs(color="Generated Cluster")
clust_4 = ggplot(wine_results) + 
  geom_point(aes(x=alcohol, y=free.sulfur.dioxide,
                 col=factor(clust_quality))) +
  labs(color="Generated Cluster")
ggarrange(clust_1, clust_2, clust_3, clust_4, 
          ncol = 2, nrow=2, common.legend = TRUE,
          legend = "right") 
```

However, if we care about the precision of the clustering, the true differences among wines are not accurately captured. Especially, we cannot match the generated clustered with the true groups as we did for color clustering, if we try to compare Figure \@ref(fig:fig6) and Figure \@ref(fig:fig7). This suggests that the actual quality clusters of points are not convex.

```{r fig7, fig.align='center', fig.cap="Features by actual labels (quality)", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
#### orginal label
clust_11 = ggplot(wine_results) + 
  geom_point(aes(x=density, y=alcohol,
                 col=factor(quality))) +
  labs(color="Actual Quality")
clust_22 = ggplot(wine_results) + 
  geom_point(aes(x=volatile.acidity, y=free.sulfur.dioxide,
                 col=factor(quality)))  +
  labs(color="Actual Quality")
clust_33 = ggplot(wine_results) + 
  geom_point(aes(x=density, y=free.sulfur.dioxide,
                 col=factor(quality)))  +
  labs(color="Actual Quality")
clust_44 = ggplot(wine_results) + 
  geom_point(aes(x=alcohol, y=free.sulfur.dioxide,
                 col=factor(quality))) +
  labs(color="Actual Quality")
ggarrange(clust_11, clust_22, clust_33, clust_44, 
          ncol = 2, nrow= 2, common.legend = TRUE,
          legend = "right") 
```

The failure of quality clustering can be confirmed again by comparing the actual number of each group and the number of wines in each predicted clusters. If the clusters are capable of classifying the seven levels quality, then the distribution of wine numbers among clusters should look similar to the one among true quality groups. Figure \@ref(fig:fig8) shows the distribution are different and thus clustering algorithms cannot precisely distinguish higher from the lower quality wines.

```{r fig8, fig.align='center', fig.cap="Counts of each cluster / quality groups", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
### distribution 
clust_5 = wine_results %>%
  group_by(quality) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = reorder(factor(quality),(-count)), y = count)) + 
  geom_bar(stat = 'identity') +
  xlab("Actual Quality") +
  ylab("Count")+
  ylim(0,3000)
clust_6 = wine_results %>%
  group_by(clust_quality) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = reorder(factor(clust_quality),(-count)), y = count)) + 
  geom_bar(stat = 'identity') +
  xlab("Predicted Clusters") +
  ylim(0,3000) 
ggarrange(clust_5, clust_6+rremove("ylab"), ncol = 2, nrow = 1) 
```

## Principal component analysis
### Color of wines
Next, we consider PCA to see if there are some principal components that can distinguish the reds from the whites, or distinguish wines of different quality. Before that, we would like to take a look at the heatmap (Figure \@ref(fig:fig9)), which shows that there exist some correlated features that might be able to be summarized by a principal component, like `residual.sugar`, `total.sulfur.dioxide`, and `free.sulfur.dioxide`.

```{r fig9, fig.align='center', fig.cap="Heatmaps of features", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
# Principal Component Analysis #
ggcorrplot::ggcorrplot(cor(wine), hc.order = TRUE)
```

The results of PCA show that the first two components can account for about half of the variations. 

```{r warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
wine_PCA = prcomp(wine, rank = 11)
summary(wine_PCA)
wine_loadings = wine_PCA$rotation %>%
  as.data.frame %>%
  rownames_to_column('features')
wine_scores = wine_PCA$x %>%
  as.data.frame() %>%
  rownames_to_column('wine_code')
wine_results = wine_results %>% rownames_to_column('wine_code')
## color ##
wine_results = merge(wine_results, wine_scores, by = 'wine_code') 
wine_plot_data_pca = melt(wine_results, id.var = colnames(wine_results)[1:16],
                          variable.name = 'PC')
```

The preliminary visualization in Figure \@ref(fig:fig10) has indicated the significant differences in principal component 1 between red wines and white wines.

```{r fig10, fig.align='center', fig.cap="Value of principal components for wines of different colors", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
ggplot(wine_plot_data_pca) +
  geom_boxplot(aes(x=color, y=value)) +
  facet_wrap(~PC) +
  labs(y = "Value of Principal Components",
       x="Actual Color")
```

Figure \@ref(fig:fig11) further confirmed that we can distinguish the reds from the whites using principal component 1: `PC1`'s scores tend to  higher on the whites than on the reds.

```{r fig11, fig.align='center',fig.cap="Principal components by actual labels (color)", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
### Groups emerge naturally from PCA
ggplot(wine_results) +
  geom_point(aes(x=PC1, y=PC2, color=factor(color))) +
  labs(y = "Principal Component 2", x="Principal Component 1",
       color='Acutal Color') 
```

### Quality of wines
Figure \@ref(fig:fig12) shows that there is no principal components that can significantly differ wines of different quality.

```{r fig12, fig.align='center', fig.cap="Value of principal components for wines of different quality", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
## quality ##
### Distributions of scores over quality
# Should look at the scores, i.e. go wine by wine or quality by quality
# what the first summary of these scores over quality?
# refernce: 【8.4】ercot_PCA.R
ggplot(wine_plot_data_pca) +
  geom_boxplot(aes(x=factor(quality), y=value)) +
  facet_wrap(~PC) +
  labs(y = "Value of Principal Components",
       x="Actual Quality")
```

However, Figure \@ref(fig:fig13) shows that principal component 2 and principal component 3 would decrease with quality on average.

```{r fig13, fig.align='center', fig.cap="Median value of principal components for wines of different colors", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
wine_plot_data_pca %>%
  group_by(quality, PC) %>%
  summarise(median_feature = median(value)) %>%
  ggplot() +
  geom_point(aes(x=factor(quality), y=median_feature)) +
  facet_wrap(~PC, ncol=3)+
  labs(y = "Median Value of Principal Components",
       x="Actual Quality") # most differed by PC2 and PC3
```

Figure \@ref(fig:fig14) shows that wines of high quality tend to have less principal component 2 and vice versa. But the pattern is not very clear and may not able to classify quality very well.

```{r fig14, fig.align='center', fig.cap="Principal components by actual labels (quality)", warning=FALSE, echo=FALSE, message=FALSE, alert=FALSE}
ggplot(wine_results) +
  geom_point(aes(x=PC2, y=PC3, color=factor(quality))) +
  labs(y = "Principal Component 3", x="Principal Component 2",
       color='Acutal Quality') 
```


